 \begin{conf-abstract}[]
 {Chase Me}
 {Drishya Thapa
 	Sukmit Thapa 
 	Joshila Joshi
 }
{}

  \indexauthors{Drishya Thapa,
  	Sukmit Thapa,
  	Joshila Joshi}
The purpose of our project was to build an online,real-time,multiplayer tag game.First we searched on app stores for two different types of games:online multiplayer games and tag games.We found that most popular tag games had multiplayer feature but not across the network(online).On the other hand,there were tons of other online multiplayer games with more advanced features.So we decided to merge these two things in our own way.Then our next aim was to find the appropriate platform to build our game and our search ended with the result "Unity 3D,a popular game development platform".As the next important thing in our project was "across the network(online)",so we began searching on the internet about how we can  implement networking on Unity 3D in an efficient way.We came across many different solutions and among them we chose "Photon Engine, a multiplayer game networking engine".In this paper we present how we built our game using Unity 3D and Photon Engine.

1.To let the user join from Facebook or as a guest.

2.To provide the user with coins.

3.To let the user play the game with:-

3.1.anyone who is online(other players who are currrently available for the game):-

-take entry fees(coins) and reward the winner with more coins.

3.2.with his/her own friends:-
-do not take entry fees(coins) but reward the winner with coins so that they can earn free coins.

4.To let the user choose the character.

5.To let the user decide where they want to play depending upon the maximum number of players that can play there:-
-two players(per game) with game time 60 seconds.
-three players(per game) with game time 90 seconds.
-four players(per game) with game time 120 seconds.

6.In the game,to let the player control his/her character which will have his/her name above it.

7.To let the user play the actual game:-
-to randomly select a chaser among the players at the start of the game.
-to display game timer for all players.
-to provide "chaser stopwatch" to each players which keeps track of the time period where that player has been the chaser.
-to detect chaser collision i.e.detect if the chaser has collided with any of the chasee.If so,make that chasee the new chaser.
-when the game time ends,to sort the timestamps which is on the "chaser stopwatch" of all players and make the player with            
least  timestamp, the winner.  

8.To handle "internet disconnect" and players leaving in the middle of the game.



In a nutshell,"Chase Me" is a tag game that can be played at real-time with multiple players across the internet which is built using Unity 3D. 
 \end{conf-abstract}