 \begin{conf-abstract}[]
 {"Episode" Recommender}
 {Sudip Dawadi
 	Suyog K.C
 	Saroj Pandey
 }
{}

  \indexauthors{ Sudip Dawadi,
  	Suyog K.C,
  	Saroj Pandey}
These days there are too many contents being produced for the TV audience stream-able online as well as airing on the TV. It is really difficult to choose from a myriad of options in what little time a viewer has to enjoy the art of TV. "Episode" Recommend-er is designed with the sole intention of helping such TV content consumer to find a suitable match for their taste. Our application recommends users to watch certain shows based on the user's interests and behavior. A sample survey will be used for reference to determine the viewing behavior its implications and the suitable recommendation algorithm for the application.

The major objectives of our project are as follows:
To perform a survey on the TV viewing habits of a sample population and determine an appropriate algorithm for recommendation based on its results.
•	To help TV viewers filter and select suitable contents based on their personal interests
•	To build an application that recommends viewers contents based on their previous watch patterns
•	To provide viewers with a breakdown of their TV viewing habit so that they can modify their behaviors as they deem reasonable

Episode recommend-er application will fill in the void that the TV audience have long felt due to choice paralysis, that occurs due to heavy production of TV content. It will help the audience select best TV shows to watch that will add meaning to their TV viewing behavior and at the same time provide objective assessment of the time they spend watching TV shows. 
 \end{conf-abstract}