 \begin{conf-abstract}[]
 {ColzMS}
 {Manoj Pahari
 Rajat Thapa
 Ujjwal Panta
 }
{pantaujjwal49@gmail.com}

  \indexauthors{Manoj Pahari,Rajat Thapa,Ujjwal Panta}
This project entitled and proposed, “ColzMS” is about the college management system over the web platform. The project is going to be built purely and only forthe use in web platform. So, basically this is a website that acts as a web application that shall facilitate staffs and students for the college management.

This website shall represent features needed to manage college such as notices, results etc.The website would also represent students-teachers platform like attendance, assignments etc. Individual profile of all members of the college will be made to provide relevant and necessary information, notices and file. It can also feature as a guide for new students and staff to get sufficient details about the college without having to refer anyone on their own.

As all student and staff need some help for  tedious task of effectively running college daily.So this project intends to accomplish these points as goals:
The general objectives of our project are:

1.	To help to know about necessary details for a new student, visitor or a staff.

2.	To help in the day to day routine and activities in college management.
\\
The specific objectives of our project are: 

1.	To keep the attendance record of students.

2.	To provide relevant notices, results, routines.

3.	To facilitate student teacher interaction.

4.	To create individual profile of students and staffs to create friendly and secure environment.

The colleges will get benefit from our application tofacilitate staffs and students for the college management by providing the features of attendance record,students-teachers interaction and individual profile of all members of the college that will provide relevant and necessary information, notices and file enhancing a collaborative environment.
This project intends to aid as a prototype for a project alike platform that would include more colleges in near future.

 \end{conf-abstract}