 \begin{conf-abstract}[]
 {Accounting for Inventory and Sales Management System}
 { Ganesh Pandey
 	Nishal Gurung
 	Pratima Sharma
 }
{}

  \indexauthors{Ganesh Pandey,
  	Nishal Gurung,
  	Pratima Sharma
  }
The project ‘Accounting for Inventory and Sales Management System’ is an extension to our minor project entitled ‘Inventory and Sales Management System’ that we completed in our third year to fulfill course requirements.

The web based project comprised of an efficient inventory and sales management system for large and small scale bookstores to help update and keep track of the inventory. The accounting feature added to the software will and aid in the transaction of sales and help in measuring, processing and communicating financial information about the organizations economic activities.

i.	To implement full accounting features on the system.

ii.	To implement notifications and alert features on the system.

iii.	To generate detailed and insightful business reports and forecast.

iv.	To synchronize the data both on cloud and on a local server. 

v.	To improve the features of inventory control.

All businesses use accounting information systems. This project helped us develop an appreciation of the role of computerized accounting software in a business environment from the perspective of end users and to understand the concepts of the integrated structure of a computerized accounting system when processing accounting transactions. 
We gained an understanding of how business transactions work in the real world and how it can be made simpler and easier through the help of technology.

\end{conf-abstract}