 \begin{conf-abstract}[]
 {Analysis on Recommendation System }
 { Aatish Sai
 	Anup Acharya
 	Deepti Baral
 	Sagar Serchan
 }
{}

  \indexauthors{ Aatish Sai,
  	Anup Acharya,
  	Deepti Baral,
  	Sagar Serchan}
On the Internet, where the number of choices is overwhelming, there is need to filter, prioritize and efficiently deliver relevant information in order to alleviate the problem of information overload, which has created a potential problem to many Internet users. Recommender systems solve this problem by searching through large volume of dynamically generated information to provide users with personalized content and services. This paper explores the different characteristics and potentials of different prediction techniques in recommendation systems in order to serve as a compass for research and practice in the field of recommendation systems.

-To analyze the existing recommendation algorithm such as
popularity model, content based, collaborative filtering, Singular
Value Decomposition (SVD).

- To analyze the learning algorithm using matrix factorization such as
Stochastic Gradient Descent (SGD) and Alternating Least Square
(ALS).

- To study about usefulness of the afore mentioned algorithms.

- To devise a theoretical approach to get better recommendation.

- To create a simple GUI based recommendation application based on
K-mean clustering algorithm (collaborative filtering)

We analysed various algorithms and found out their potential advantage and disadvantage in various situations.
 
\end{conf-abstract}