 \begin{conf-abstract}[]
 {Farmer Market }
 {Anup Sharma
 	Samit Sherchan
 	Bikky Bhujel
 	Subash Chalise
 }
{}

  \indexauthors{Anup Sharma,
  	Samit Sherchan,
  	Bikky Bhujel,
  	Subash Chalise}
This project is designed to introduce bigger market for farmers and give farmers power to determine price without any middlemen, so that they can get best monetary return from their crops. It has been designed to help farmer with “supply and demand of market”, so that they can have the overview of current market. It’s goal is also to educate farmer about modern techniques of farming. It will help to create a smooth relation between agricultural producer and consumer directly. The project’s vision is to provide farmers with better return from their crop so they can invest and diversify their business.
\\
Program will have these four main objectives :

1) Provide latest information about the modern techniques and information in farming .

2) Provide latest market “supply and demand " state

3) Provide farmer with bigger market

4) Connect directly between producer and consumer

From our survey we found out that farmers are cheated by the middleman between the shopkeepers and the farmers. So for this type of problem we created this web-based application where users can directly buy goods produced by the farmers or users can post their products. It gives information for reaching and interacting with customer like online marketing. 

Farmers in the rural areas are unable to sell their products to whomever they want to sell. So our application makes them easy to sell or buy as well as advertise their products. Our application 'Farmer Market' provides a convenient approach for customers to carry out selling and buying activities related to farming.

 \end{conf-abstract}