 \begin{conf-abstract}[]
 {Ghar Jagga }
 { Rabin Senchuri
 	Bijay Gurung
 	Abhishek Poudel Chhetri  
 	Prameet Bhakta Acharya
 }
{}

  \indexauthors{ Rabin Senchuri,
  	Bijay Gurung,
  	Abhishek Poudel Chhetri  ,
  	Prameet Bhakta Acharya}
 “Ghar Jagga” is a web based application through which a user can perform the activities like buying and selling of land and houses. In this web application, the user can access information and advertise their real estate properties. The admin user can change and update the information regarding the property selling and buying. The main objective of this web application is to provide the user a convenient and flexible procedure to advertise a list of real estate properties online and help them choose a best one to buy from a list of properties.
 
 -To provide a means to the user (seller) to publicize and advertise his/her real estate properties.
 
 -To allow user (buyer) to search o browse particular land or houses from a list of houses and lands.
 
 -To provide an interface so that the use can compare between two different real estate properties.
 
 As you all known that our project is a web based application which can be done by online for selling, buying. From our survey, people were betray by the agent. Agents are also made for earning money by doing good or bad work but many of the agents betrayed their customer by showing other’s land, possibility of firing by taking money of customer and becoming contactless. So for this type of problem, we created this project for the helpful of people. It means dealing of goods and services through the electronic medium and internet. Our project is also like e-commerce sites doing electronically which makes easier in buying, selling and advertising. It facilitates new type of information based business processes for reaching and interacting with customer like online advertising and marketing, online order taking and online customer service. Objective are fulfilled.
 
\end{conf-abstract}