 \begin{conf-abstract}[]
 {NepaliMade}
 {Bibek Kumar Gupta
 	Paras Bhujhel
 	Saroj G.T.
 	Sijan Shrestha
 }
{}

  \indexauthors{Bibek Kumar Gupta,
  Paras Bhujhel,
  Saroj G.T.,
  Sijan Shrestha
  }
“Nepali made” is an E-commerce site for browsing, searching and buying Nepali local goods and materials. This Project aims to promote traditional and modern goods and materials that are produced locally in Nepal. The basic objective of this project is to ease the process of buying and selling local goods through an online portal. The project itself acts as a middle-man by creating a link of business between the local sellers and buyers. 

This project is going to be totally built on web using PHP Framework Laravel. The User Interface part will be taken care by CSS framework Bootstrap and a taste of JavaScript will be introduced to make the product more interactive and responsive. This Project is going to be completed by a Group of 4 Members each working on Version Control Platform Git to track each other’s activity and make everything more productive and effective. 

•	- To build a feature rich e-commerce site for buying Nepali Goods.

•	- To promote locally made and crafted traditional goods and materials of Nepal.

•	- Main focus is on enhancing the Tourism sector of Nepal and add some boost to the tourism industry.

•	- To provide efficient management of users divided into general customers, merchants and Super Admin.

The project aims to promote Nepali products and goods to Nepali consumer Market and Tourism market via Business-to-business ecommerce Model.
\end{conf-abstract}