 \begin{conf-abstract}[]
 {Outsourcing Nepal}
 { Mahesh Prasad Josi
 	Rahul Subedi
 	Rajan Lamsal
 	Top Kumar Purja
 }
{}

  \indexauthors{Mahesh Prasad Josi,
  	Rahul Subedi,
  	Rajan Lamsal,
  	Top Kumar Purja
  }
There are many freelancing platforms and outsourcing companies which provide online outsourcing jobs in the global market each of them with different set of features. But most of them are not easily accessible in Nepal. If some, they also controlled and linked through broker companies due to which the developers who works for those companies are not benefited as per for their hard work.
In the context of Nepal, there is no specific platform where normal people can go and learn IT subjects and earn through the knowledge they achieve. So this platform is dedicated to Nepali youth who wants to learn and earn from their own home.
\\
The objective of this project is to provide Nepalese people access to learn and earn. Other objectives are:

•	Client and contractor registration and verification.
 
•	Post a job and hire a contractor.

•	Apply application and get job.

•	Easy hiring and working environment.

•	Learning new subjects from the guidelines of other Nepalese                         experts.*(OPTIONAL)
\\
   Most of Nepalese IT companies are based on outsourcing works. Some of them are doing excellent business. But developers are not being much benefited by those jobs. 
Outsourcing Nepal is a platform for those developers and other people, who wants to work on their own. 

\end{conf-abstract}