\begin{conf-abstract}[]
{Chameleon}
{
               Binod Khatri
                Sambhu Sai
              Sumit Shrestha
             Yam Bahadur Gurung
}
{2009}
\indexauthors{
               Binod Khatri,
                Sambhu Sai,
              Sumit Shrestha,
             Yam Bahadur Gurung
}

With the advent of internet, online shopping has evolved as a multi-dimensional business
that includes features like different product searching, comparison of price, electronic
shopping cart, electronic payment, etec. However, it lacks some of the features that are 
available in traditional shopping mall which is personalized shopping experience namely 
customer behaviour tracking and personalized page generation. Chameleon- an adaptive shopping
mall is the enterprise level distributed shopping system which performs data mining for analyzing customer 
behavior dynamically to generate an auto customized web pages for the particular customer. This system focuses
on different forms of adaptation in electronic catalogs and shopping malls and their demands on user modeling
considering different types of user data, the privacy and confidence of the user as well as the need of
simple integration and reuse of user modeling and adaptation components. This system provides the solution 
to the  existing problems in the online shopping systems through the personalized item recommmendation based on
the customer beahviour. Adaptability is the core of the system and thus it is an addition to the list of adaptive 
websites. The following report exlains the various aspects of the project including research done, artifacts developed and 
new findings. This report evalates various existing techniques used in the adaptive websites for shopping
purposes and explains the implementation of the best technique with relevant modification. This report also recommends
new problems solving approaches for the modern complex enterprise level online business.
\end{conf-abstract}

   