 \begin{conf-abstract}[]
{Mass Mailing System}
{
Amber Gurung
}
{2014}
\indexauthors{
Amber Gurung
}
Information technology has clocked up huge part of human life.
Reduction of time, better administration operation, accurate data analysis
and report headed human to depend more on Information Technology.
The proposed system also include all of the above Information Technology
attributes. Particularly, this system is engineered in order to replace
current individual mailing system.

The sequentially structured report makes easy and convenience to the
readers. The whole report is sectioned into several chapters depending
upon the scope and difference each chapter is further broken down into 
several heading.

Chapter one demonstrates introduction part to Client's Organization and
objective of the report. Chapter two demonstrates problem domain,
related technologies and elaboration of new system.Chapter three
demonstrates solution consideration, software development and
methodology. In design part, we give short description of design
with the MMS design too. In Implementation section we clarify the
implementation way and real file and working mechanism.By Testing
the each part of the MMS design too. In Implementation section, we clarify 
implementation way and real file and working mechanism. By Testing 
each part of the MMS,we confirm whether it successfully works in
real filed or not. Finally project is concluded with the future scope and 
development.After reading this report the reader will understand the
project guidelines with overall outlines of the project and the techniques
of implementation of project easily in real time.
  \end{conf-abstract}