 \begin{conf-abstract}[]
{Mato}
{
Bibek Thapa
Binay Subedi
Bipin Subedi
Naresh GC
}
{2015}
\indexauthors{
Bibek Thapa,
Binay Subedi,
Bipin Subedi,
Naresh GC
}
Nepal is predominantly an agricultural country and agriculture is the foundation for sustainable economic development and the major source of income for the people. Soil analysis, plantation, weeding and harvesting time for the crops, land to fertilizer ratio are the most important factors for farming. MATO is an effort for providing these information in the form of web application as Nepalese farmers are still dependent on traditional and manual practices for farming.

MATO is a web based software application developed using PHP and MySQL Server. MATO is primarily focused on suggesting the best crops to the users based on the PH value of their soil without having to consult with agricultural experts. MATO facilitates users by providing the information about the types and amount of fertilizers to be used in order to increase the productivity of the soil. MATO suggests the suitable time period for planting, weeding and harvesting the crops based on weather analysis of the corresponding region. MATO also includes charts and graphs associated with production of various crops which help farmers to select the trending crops that have better economic vlaues. MATO enables farmers to get all these facilities from any place just by accesing into the internet and farmers do not require the experts for solving their agriculture related queries.
  \end{conf-abstract}