 \begin{conf-abstract}[]
 {Ayo Gorkhali }
 {Bishal Pun \textsuperscript{1}
 	Siddhant Pageni \textsuperscript{2}
 	Susan K.C. \textsuperscript{3}
 }
{\textsuperscript{1} bishalpun2013@gmail.com 
	\textsuperscript{2} siddhantpageni@gmail.com 
	\textsuperscript{3} susan.kc13@gmail.com}

  \indexauthors{Bishal Pun ,
  	Siddhant Pageni ,
  	Susan K.C.}
The AYO GORKHALI is a 3D RPG game that will promote Nepalese History. The story has been adopted from the first battle of the Anglo-Nepalese War of 1814-1816AD (Nalapani War). This war is historically important to Nepalese people because it established the Gurkhas’ reputation as warriors. To preserve and promote this valor and esteem, this game was developed. The main character is “Dorje”, a typical Gorkhali soldier born and raised in a poor family who lives by his principles and lives to protect his family and country, whose main mission is to make a way out of the fort for his seventy surviving members of the garrison and safely return back to his family. One of the main focus on our game will be to build and enable AIs in characters so that their communication and attack looks realistic.

a)	To complete game mechanics and game logic using some dummy placeholders in the first release.

b)	To develop and optimize AI for opponents so that their attack strategy looks realistic.

c)	To make the game visually appealing by replacing the placeholders with real assets.

d)	To add visual effects and sound effects in the final release.

e)	To enable VR and export the game for oculus.

As a part of academic requirement, we developed this game with the theme of Nalapani war fought between Nepali Gurkhas' and British. During the game development time frame, we studied and applied various aspect of game development such as modeling 3D characters, Rigging the characters, Animating the characters, Level design, Sound effects, Visual effects, Game Optimization, Enemy AI development, UI design, Gameplay design, Scripting etc. 

 \end{conf-abstract}